Distributed Topology Discovery in Self-Assembled Nano Networks

### 2014-02-18 trunk/PAPER/disr.tex
fixes

\label{sec:disr_concepts}
The main concept behind the kind of turn prohibition we want to
achieve is the \emph{segment}. A segment $S_y$ is basically a path of consecutive
nodes and links, starting with a link attached to a node belonging to
a different segment $S_x$ and ending with a link attached to a
node of another segment $S_z$. In other words, a segment
a path between connecting two other different segments. The example
in Figure~\ref{fig:segments} shows the segment with id $1.4$, starting
with a link connected to the node $9$, the going through nodes
$4$,$3$,$2$ and ending with the link connected to the node $1$. Other
segments depicted are $9.2$ (link,node $10$,link) and $9.3$
(link from $9$ ,$8$,link,$7$,link,$6$,link,$5$,link to the $1$). Note
also that start/ending link can coincide and a segment can also be
formed by one single link (e.g. in $7.2$ or $5.4$).
An exception to the rule that a segment must connect two other
segments is the first segment established in the network, called
\emph{starting segment} which is a loop beginning/ending on the same
node.

@@

\section{Detailed Node behavior Model}
\label{sec:execution_model}

@@

The \emph{LED} variables at each node
($segID$,$visited$,$tvisited$,\emph{link\_visited[]},\emph{link\_tvisited[]})
are initially set as \texttt{NULL}, so the node and each of its links
are considered as free.
The only node that makes exception is the bootstrap node, initialized
in the \emph{Bootstrap} status. All the subsequent events happening at
each node are the consequence of its current dynamic status (DBS), the
packets received and the internal status represented by the
\emph{LED}. Note that in the following, when using expression like
``has a free link'' or ``free node'' we will assume the relationship between 
$LED$ and $DBS$ discussed in Section~\ref{sec:disr_data}. Further, for
each packet type all the cases not explicitly listed can simply be
ignored since are associated to invalid/inconsistent events of the
\disr{} execution model. A complete list of these cases can be checked
in the environment simulator source code at~\ref{nanoxim}.

\subsection{Receiving a \texttt{STARTING\_SEGMENT\_REQUEST}}

The request for the first segment should be managed differently since
all nodes (except the bootstrap one) must forward the packet using a
broadcasting mechanism. This is necessary since the request packet must
return the bootstrap node.
When a node receives a \texttt{STARTING\_SEGMENT\_REQUEST}, the
following cases can happen:

@@

\subsection{Intra-node vs Inter-node parallelism}
In the processes described above, we assumed that each node in the
\emph{Assigned} status can start a find segment process by injecting a
\texttt{SEGMENT\_REQUEST}. However, a more accurate decision when
defining \disr{} should be made in order to decide whether or not the
node must actually perform this action.  The point above is is
strictly related to the general question: which level of “parallelism”
should we allow in \disr{} ? The adopted approach is that, although
the nature of \disr{} itself is intrinsically parallel, the use of
parallelism makes things work in a more complex way. In other words,
\disr{} is parallel when needed, but it does not exploit parallelism
as an “improving feature”. When not needed, things should be
serialized. For example: when a node is “ready searching” could start
several find segment process associated to the same segment, one for
each free link. But serializing this by investigating the free links
in order could be a simplest solution. We refer to this saying that we
avoid intra-node parallelism.  Note that while intra-node parallelism
can be avoided, trying to avoid inter-node parallelism could be more
complex than allowing the parallelism itself. Imagine for example the
effort of trying to coordinate nodes so that an unique finding node
process is actually running in the whole subnet. Thus, in contrast to
the intra-node parallelism, the inter-node parallelism is a structural
property of the \disr{} algorithm and should not be avoided.
%------------------------------------------------------------------------------

>>>>

\label{sec:disr_concepts}
The main concept behind the kind of turn prohibition we want to
achieve is the \emph{segment}. A segment $S_y$ is basically a path of consecutive
nodes and links, starting with a link attached to a node belonging to
a different segment $S_x$ and ending with a link attached to a
node of another segment $S_z$. In other words, a segment
a path between connecting two other different segments. The example
in Figure~\ref{fig:segments} shows the segment with id $1.4$, starting
with a link connected to the node $9$, traversing nodes
$4$, $3$, $2$ and ending with the link connected to the node $1$. Other
segments depicted are $9.2$ (link,node $10$,link) and $9.3$
(link from $9$, node $8$, link, node $7$, link, node $6$, link, node $5$, link to the $1$). Note
also that start/ending link can coincide and a segment can also be
formed by one single link (e.g. in $7.2$ or $5.4$).
An exception to the rule that a segment must connect two other
segments is the first segment established in the network, called
\emph{starting segment} which is a loop beginning/ending on the same
node.

@@

\section{Detailed Node Behavior Model}
\label{sec:execution_model}

@@

The \emph{LED} variables at each node
($segID$,$visited$,$tvisited$,\emph{link\_visited[]},\emph{link\_tvisited[]})
are initially set as \texttt{NULL}, so the node and each of its links
are considered as free.
The only node that makes exception is the bootstrap node, initialized
in the \emph{Bootstrap} status. All the subsequent events happening at
each node are the consequence of its current dynamic status (DBS), the
packets received and the internal status represented by the
\emph{LED}. Note that in the following, when using expression like
``has a free link'' or ``free node'' we will assume the relationship between 
$LED$ and $DBS$ discussed in Section~\ref{ssec:disr_data}. Further, for
each packet type all the cases not explicitly listed can simply be
ignored since are associated to invalid/inconsistent events of the
\disr{} execution model. A complete list of these cases can be checked
in the environment simulator source code at~\cite{nanoxim}.

\subsection{Receiving a \texttt{STARTING\_SEGMENT\_REQUEST}}
The request for the first segment should be managed differently since
all nodes (except the bootstrap one) must forward the packet using a
broadcasting mechanism. This is necessary since the request packet must
return the bootstrap node.
When a node receives a \texttt{STARTING\_SEGMENT\_REQUEST}, the
following cases can happen:

@@

\subsection{Intra-node vs Inter-node parallelism}
In the processes described above, we assumed that each node in the
\emph{Assigned} status can start a find segment process by injecting a
\texttt{SEGMENT\_REQUEST}. However, a more accurate decision when
defining \disr{} should be made in order to decide whether or not the
node must actually perform this action.  The point above is is
strictly related to the general question: which level of
parallelism should we allow in \disr{}? The adopted approach is that, although
the nature of \disr{} itself is intrinsically parallel, the use of
parallelism makes things work in a more complex way. In other words,
\disr{} is parallel when needed, but it does not exploit parallelism
as an ``improving feature''. When not needed, things should be
serialized. For example: when a node is “ready searching” could start
several find segment process associated to the same segment, one for
each free link. But serializing this by investigating the free links
in order could be a simplest solution. We refer to this saying that we
avoid intra-node parallelism.  Note that while intra-node parallelism
can be avoided, trying to avoid inter-node parallelism could be more
complex than allowing the parallelism itself. Imagine for example the
effort of trying to coordinate nodes so that an unique finding node
process is actually running in the whole subnet. Thus, in contrast to
the intra-node parallelism, the inter-node parallelism is a structural
property of the \disr{} algorithm and should not be avoided.
%------------------------------------------------------------------------------
